Sperm do not evolve to collaborate in female meiotic drive.

### 2014-05-16 writeup_and_notes/male_dependent_drive.tex
changes to abstract

%FIgures 
{\bf Abstract:}
Because only one of four products of female meiosis is transmitted to offspring, oogenesis is particularly
	 susceptible to genomic conflicts arising when an allele gains in frequency at a cost to organismal fitness. 
In fact, many facets of oogenesis have been interpreted as mechanisms of protection against genomic outlaws. 
Why then is female meiosis often left uncompleted until after fertilization - 
	potentially providing an opportunity for sperm to meddle with its outcome and facilitate meiotic drive? 
The population genetic theory presented herein suggests that
	sperm nearly always evolve to increase the fairness of female meiosis when possible. 
These results are consistent with current knowledge of sperm-dependent meiotic drivers, 
	and suggest that the requirement of fertilization for the completion of meiosis may represent 
	yet another mechanism of female meiosis designed to prevent meiotic drive.
\newpage

>>>>

%FIgures 
{\bf Abstract:}
Because only one of four products of female meiosis is transmitted to offspring, oogenesis is particularly
	 susceptible to genomic conflicts arising when an allele
         spreads at a cost to organismal fitness. 
In fact, many facets of oogenesis have been interpreted as mechanisms of protection against genomic outlaws. 
Why then is female meiosis often left uncompleted until after fertilization - 
	potentially providing an opportunity for sperm to meddle with its outcome and facilitate meiotic drive? 
The population genetic theory presented herein suggests that
	sperm nearly always evolve to increase the fairness of female meiosis when possible. 
These results are consistent with current knowledge of sperm-dependent meiotic drivers, 
	and suggest that the requirement of fertilization for the completion of meiosis may represent 
	yet another mechanism of female meiosis designed to prevent meiotic drive.
\newpage
